|

### 2021-11-15 paper/dcpo_demsupport.Rmd

```{r mocResult-pureAJPS, eval=FALSE}
df_correct_clsAjps <- purrr::map(1:900, function(anEntry) {
    correct_cls_ajps[[anEntry]] %>%
        plm::pdata.frame(index = c("country", "year"))
})

@@

saveRDS(mocresult_correctAPSR,
        file = here::here("ouput", "estimates_moc_correctAPSR.RDS"))
```

>>>>

```{r mocResult-pureAJPS}
df_correct_clsAjps <- purrr::map(1:900, function(anEntry) {
    correct_cls_ajps[[anEntry]] %>%
        plm::pdata.frame(index = c("country", "year"))
})

@@

saveRDS(mocresult_correctAPSR,
        file = here::here("output", "estimates_moc_correctAPSR.RDS"))
```
